A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Comment explanation

Unlike Javascript, R packages also call native code for access to efficient
numerical and statistical routines. We intercept all calls to R functions and
native functions from the programs and \eval calls. In the whole corpus there
are \AllClosureCallCount calls to R functions and \AllNativeCallCount to native
code. Of those, \eval contribute to only \EvalClosureCallCount calls to R
functions and \EvalNativeCallCount to native code.

>>>>

%Unlike Javascript, R packages also call native code for access to efficient
%numerical and statistical routines. We intercept all calls to R functions and
%native functions from the programs and \eval calls. In the whole corpus there
%are \AllClosureCallCount calls to R functions and \AllNativeCallCount to native
%code. Of those, \eval contribute to only \EvalClosureCallCount calls to R
%functions and \EvalNativeCallCount to native code.
